Syntax Is All You Need: A Universal-Language Approach to Mutant Generation

### 2023-03-28 paper/main.tex

\begin{table}[hbtp]
  \centering
  \caption{Overview of Mutation Testing Tools.}
  \label{tab:mutationtools}

  \begin{tabular}{|c|c|r|}
  \hline
  \textbf{Language} & \textbf{Tool} & \textbf{LOC}  \\
  \hline
  \multirow{2}{*}{Python}  & Mutmut &	3870  \\\cline{2-3}
      & cosmic-ray & 4599 \\ \hline
  \multirow{2}{*}{Java}  & PIT &	59577  \\\cline{2-3}
      & LittleDarwin & 22359 \\ \hline
      Rust & Cargo-Mutants & 7020 \\\hline
    C++ & Dextool & 38611 \\\hline
    \hline
      ALL & Our Tool & 2680 \\\hline
  \end{tabular}
\end{table}

>>>>

\begin{table*}[hbtp]
    \centering
    \caption{Overview of Mutation Testing Tools. universalmutator has singificantly fewer lines of code than any of the single language tools.}
    \label{tab:mutationtools}

    \begin{tabular}{|c|c|c|r|}
    \hline
    \textbf{Language} & \textbf{Tool} & \textbf{URL} & \textbf{LOC}  \\
    \hline
    \multirow{2}{*}{Python}  & Mutmut & https://github.com/boxed/mutmut & 3870  \\\cline{2-4}
        & cosmic-ray & https://github.com/sixty-north/cosmic-ray & 4599 \\ \hline
    \multirow{2}{*}{Java}  & PIT & https://github.com/hcoles/pitest & 59577  \\\cline{2-4}
        & LittleDarwin & https://github.com/aliparsai/LittleDarwin & 22359 \\ \hline
        Rust & Cargo-Mutants & https://github.com/sourcefrog/cargo-mutants & 7020 \\\hline
        C++ & Dextool & https://github.com/joakim-brannstrom/dextool & 38611 \\\hline
        ALL & universalmutator & https://github.com/agroce/universalmutator & 2244 \\\hline
    \end{tabular}
    \end{table*}
